Supplementary Material

### 2022-11-10 paper/paper/SPIE/article.tex
[WIP]

\subsection{Normalization}
There was no visible effect of normalization on mAUROC distributions at any
summary level.

@@

\subsection{Effect of Slicing}
Features were most predictive when using either the largest 5 or 10\% or middle
25\% ("max-05", "max-10" and "mid-25" in Figure
\ref{S-fig:best-params-slicing}), and least predictive when features primarily
involved the smallest eigenvalues.

@@

>>>>

\subsection{Normalization}
There was no visible effect of feature normalization on mAUROC distributions.

@@

\subsection{Effect of Slicing}
Features were slightly more predictive when using either the largest 5 or 10\% or middle
25\% ("max-05", "max-10" and "mid-25" in Figure
\ref{S-fig:best-params-slicing}), and least predictive when features primarily
involved the smallest eigenvalues.

@@

\section{Discussion}

In this study, eigenfeatures inspired by RMT and derived from the eigenvalues
of the full, whole-brain voxelwise fMRI correlation matrix, were found to have
predictive utility across a wide variety of phenomena. Compared to simple
baseline reductions of the fMRI data, these eigenfeatures had more consistent
predictive utility, and a higher maximum predictive potential (Figures
\ref{fig:main-results}-\ref{fig:largest}).  In addition to evidence from
previous studies
\cite{sebaRandomMatrixAnalysis2003,wangRandomMatrixTheory2016,matharooSpontaneousBackpainAlters2020}
this suggests RMT may be a useful analytic and theoretical tool for
understanding functional connectivity.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6.5in]{unfolded_duloxetine_nopain.png}
\end{tabular}
\end{center}
\caption
{ \label{fig:unfolded} Raw eigenvalues and unfolded eigenvaleus (polynomial degree 9) for \textit{Osteo} dataset \code{duloxetine v nopain} classification task.}
\end{figure}

When RMT-based eigenfeatures were most predictive

### 2022-11-10 paper/paper/SPIE/supplementary.tex
[WIP]

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{fine_feature_group_by_predictive_subgroup_classifier.png}
\end{center}
\caption
{ \label{fig:fine-classifier}
AUROC distributions across coarse feature groupings and predictable comparison tasks, by classifier.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{rmt_feature_auroc_by_trim.png}
\end{center}
\caption
{ \label{fig:fine-trim}
Distributions of mAUROCs for unfolding-dependent RMT features, by degree.}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{fine_feature_group_by_predictive_subgroup_classifier.png}
\end{center}
\caption
{ \label{fig:fine-classifier}
AUROC distributions across fine feature groupings and predictable comparison tasks, by classifier.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{rmt_feature_auroc_by_trim.png}
\end{center}
\caption
{ \label{fig:fine-trim}
Distributions of mAUROCs for unfolding-dependent RMT features, by trimming.}
\end{figure}
